\documentclass[9pt]{article}
\usepackage[margin=0.9in]{geometry}
\geometry{a4paper}
\pagenumbering{gobble}

\begin{document}
\noindent{\Large{Raman Yachi Mathur}}
\hfill
\Large{Japanese citizen w/ US work authorisation}
\Large{\flushleft{+1 215-909-1925}
\hfill
\Large{ramanyachi@drexel.edu}
%\rightline{\LARGE{US work authorisation}}
\rule{\textwidth}{0.8pt}
\\

\vspace{0.2in}
\large{\textbf{\centerline{EDUCATION}}}\\
\vspace{0.2 in}
\noindent{\textbf{Drexel University}, Pennsylvania}
\hfill
Sep '16 - June '21\\
\vspace{0.05 in}
S.B in Computer Engineering. Minor in Japanese\\ %. GPA: \texttt{3.02}\\
\vspace{0.03 in}
Recipient of A.J Drexel Scholarship\\
\vspace{0.03 in}
Club Soccer player, NIRSA Division Champs\\
% Relevant Coursework:\\
% \vspace{0.03 in}
% ECE204: \textit{Microcontrollers}, CS265: \textit{Advanced Programming Techniques}, MATH221: \textit{Discrete Math}, ECE201: \textit{C Programming}, ECE200: \textit{Digital Logic}, CS270: \textit{Mathematical Foundations of Computer Science}\\
\vspace{0.1 in}
\noindent{\textbf{Woodstock School}, India}
\hfill
August '14\\
\vspace{0.03 in}
Graduated with high honours. ACT w/ writing: 34/36\\
\vspace{0.03 in}
Varsity Soccer. AP Scholar with Distinction\\
\vspace{0.2 in}
\large{\textbf{\centerline{RELEVANT EXPERIENCE}}}\\
\vspace{0.2 in}
\noindent{\textbf{Quantum Software engineering intern at Elyah.io}, Tokyo}
\hfill
Nov '19 - Jan '20\\
\begin{itemize}
\setlength\itemsep{0.01em}
\item[--]Contributed to a linear-algebra back-end. Fitted to simulate quantum circuits and algorithms. Written in Rust, deployed via WebAssembly.
\item[--]Designed and implemented a proprietary algorithm that computes unitary matrices for N-bit-controlled quantum operations. Written in Rust.
\item[--]Served as translator/liaison between the start-up and Japanese corporations interested in quantum computing. 
\end{itemize}
\noindent{\textbf{R\&D Intern at Johnson Matthey \textbar\ Clean Air}, Pennsylvania}
\hfill
%2014\\
%Paper titled "Gene therapy as a means to treat cancer" won first prize among submissions from across India. Researched viral-vectors effectiveness in nucleic acid delivery, to determine feasibility for inducing apoptosis in tumour cells. Awarded a stipend, and invited for a month of research.\\
Sep '18 - April '19\\
\begin{itemize}
\setlength\itemsep{0.01em}
\item[--]Developed novel engine control catalysts via fundamental research and tailored synthesis methods.
\item[--]Analysed data from myriad testing methods (XRF, IV Vis etc.) to determine catalysis efficiency and feasibility in scaling. Worked extensively with Excel Macros.
\item[--]Collaborated with scientists from the Americas, EU, Japan and India on internal and external projects.
\end{itemize}
\vspace{0.1 in}
\noindent{\textbf{Research Scholar at University of Sussex}, UK}
\hfill
April '17 - Sep '17\\
\begin{itemize}
\setlength\itemsep{0.01em}
\item[--]Studied perovskite solar cells, and how materials such as Zinc Oxide nanorods and graphene-oxide / graphene composites can be used to improve photoconversion efficiency.
\item[--]Researched methods of graphene synthesis and deposition that paved way for a novel perovskite solar cell architecture.
% \item[--]Constructed and programmed an Arduino-controlled spin coater for solar cell fabrication under a vacuum.
\end{itemize}
%\vspace{0.1 in}

\large{\textbf{\centerline{SKILLS}}}\\
\vspace{0.2 in}
\textbf{Languages:}
C, Rust, Python, Ruby, MATLAB, \LaTeX, Arduino IDE, Processing.js \\
 \vspace{0.03 in}
\textbf{Spoken Languages:}
Native level fluency in Japanese, English and Hindi.\\
\vspace{0.2 in}
%\large{\textbf{\centerline{INTERESTS}}}\\
%\vspace{0.2 in}
%Sustainability, computation and urban planning, cooking: worked as a line-cook in multiple Tokyo restaurants, reading and writing fiction

\end{document}